---
output: rmarkdown::github_document
---

# sanipy

Bring some sanity to R when working with Python via reticulate

## Description

A set of utilities and helpers that make using Python via `reiculate` a bit saner.

See <https://rud.is/b/2018/08/04/digging-into-mbox-details-a-tale-of-tm-reticulate/> for some functionality or look at the examples in the manual pages.

## What's Inside The Tin

The following functions are implemented:

Stucture inspection helpers:

- `pstr`:	Compactly Display the Structure of a Python object
- `pynames`:	(All) The Names of a Python Object

Strng helpers:

- `get_chr`:	Retrieve a value from a Python 'dict' as a character
- `utf8_decode`:	Decode a Python structure and retrieve a UTF-8 encoded value from it

Documentation helpers:

- `py_doc`:	Use built-in 'pydoc' to get the Python HTML manual page for a given object
- `readthedocs`:	Use "Read the Docs" to get help on a Python module/object

General Utility:

- `%|0|%`:	Default value for an object length being 0

## Installation

```{r eval=FALSE}
devtools::install_git("https://gitlab.com/hrbrmstr/sanipy.git")
# or
devtools::install_github("hrbrmstr/sanipy")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(sanipy)

# current verison
packageVersion("sanipy")

```

